\documentclass[../report.tex]{subfiles}
\graphicspath{{\subfix{../image/}}}

\begin{document}

\subsection{Forklift Connectivity and Communication}
To make the forklift usable as an distribution system, users should be
able to communicate with the forklift other than by the means of code or 
a wire connection. Hence, a wireless connection is desirable. The chosen
microcontroller enables for different options for wire
\begin{table}[ht]
\centering
    \begin{tabularx}{\linewidth}{c|L|L|L|c}
        \multicolumn{4}{c}{Options for connectivity}\\
        \hline
        \textbf{\#} & \textbf{Possible solution} & \textbf{Advantages} & \textbf{Disadvantages}\\
        \hline
        1.1&Bluetooth&
        \begin{itemize}
            \item Supported by ESP-IDF
            \item Fast and wireless
        \end{itemize}&
        \begin{itemize}
            \item Unlikely to be used by real world forklift (unless for navigation)
            \item Low range
        \end{itemize}
        \\\hline
        1.2&http-Server& \begin{itemize}
            \item Supported by ESP-IDF
            \item Fast and wireless
            \item Simple and modifiable interface as Web-Page
            \item More focus on the essential part while coding
            \item Easy to run asynchronous
        \end{itemize} & \begin{itemize}
            \item Less security than https-Server 
            \item requires WiFi-Network
        \end{itemize} 
        \\
        \hline
        1.3&https-Server& \begin{itemize}
            \item Supported by ESP-IDF
            \item Fast and wireless
            \item Higher security than http-server
            \item Simple and modifiable interface as Web-Page
            \item Easy to run asynchronous
        \end{itemize} & \begin{itemize}
            \item More complicated to code than http
            \item requires WiFi-Network
        \end{itemize} 
        \\
        \hline
        1.4&ESP-NOW
        
        Protocol for inter-board wireless communication
        &\begin{itemize}
            \item Supported by ESP-IDF
            \item Fast and wireless
            \item Long range (500m)
        \end{itemize}
        &
        \begin{itemize}
            \item Needs two ESP-boards - hence one connection to a PC meaning additional program
            \item Not as much documentation available
        \end{itemize}
        
    \end{tabularx}
\caption{Wireless methods}
\label{tab:my_label}
\end{table}

These four options are available for wireless communication. The choice 
for wireless communication is the http-Server. The http-Server provides
certain advantages over the other option listed in the table about wireless 
methods. The two server options (http and https) provide the ability
to run communication defacto in the background. Moreover,
servers can host a webpage. A webpage is the perfect way to interface
with the prototype forklift. Users of the distribution system
can interface without needing to install additional software. 
Furthermore, the interface can quickly be adapted to fit current
needs without having to update the software on each employee's device that
might need to specify a drop-off location.

\quad

\subsubsection{http-Server or https-Server}
This project is not a coding-only or networking project. So a focus on the 
implementation of the more sophisticated server protocol would
be out off focus here. Moreover, there are no severe security concerns. 

\end{document}
