\documentclass[../report.tex]{subfiles}
\graphicspath{{\subfix{../image/}}}

\begin{document}
One of the main focuses of this third semester project is analog electronics. Electronics bring the software and the mechanical part together. 
The software needs feedback from the analog world. It needs to know how heavy the load is and
whether there is an obstacle in front. Furthermore, all the smart digital electronics need to be powered. 
But when powering everything from a battery the current state of the battery has to be evaluated.
All these tasks are necessary to guarantee safe operations.

\quad
The tasks include the following:

\begin{itemize}
    \item Project requirements 
    \item Interfacing the analog load cells
    \begin{itemize}
      \item Loadcell Circuit Design
      \item Loadcell PCB Design
    \end{itemize} 
    \item Motor Drivers
    \begin{itemize}
      \item Motor Driver PCB Design
    \end{itemize}  
    \item Analog IR-Sensors for navigation
    \item Multiplexer for IR-Sensor interfacing
    \item Power Supply and Monitoring of Battery Voltage
    \item \begin{itemize}
      \item VeroBoard Design
    \end{itemize}
\end{itemize}

\subsection{Fullfilling the project requirements}
The project tasks given this semester include the usage of at least two analog sensors
and at least one analog filter. In this project there are two arrays of
IR-sensors - each counting 8 individual sensors with analog output - and 
an self-designed circuit fusing the output of 4 analog loadcells and amplifying 
it up. The following subsection will not only elaborate on the decision making
behind them, but also on the research and the working of the final product. 
  
\end{document}