\documentclass[../report.tex]{subfiles}
\graphicspath{{\subfix{../image/}}}

\begin{document}
\subsection{Individual evaluation}
A short evaluation of the project from each member in their own opinion. This is used to improve
upcoming projects, to prevent making the same mistakes again.

\textbf{Henrik:}
The project for me has been a very good experience. I was able to apply the knowledge
I learned over the last 3 semesters in every part of mechatronics. I did mechanical
design, coding and circuit design. Especially, I enjoyed working even more
with the engineering method and applying it to the various parts of mechatronics. 
It was also pleasing to see how far we have gotten with our skills and to go out of the comfort zone with circuit design. What I would change for the
next project, is to make a better wiring plan before and learn even more about PCB making.
Working with LaTeX was not a pleasant
experience, as I think it is unnecessary overcomplication. Nonetheless, I enjoyed learning something new.


\textbf{Laura:}
Write here

\textbf{Boti:}
This project was the most successful for me personally. My work was divided well between the different disciplines
and still went in depth with most of them. I gained the most valuable experience in team management, which is perhaps one of
my weak points, all things considered.

\textbf{Felix:}
In this project I was able to fuse and apply the knowledge gathered from the previous semesters, resulting in better 
workflow and communication with the group. The initial idea of making an autonomous forklift was also a good fit 
in my opinion, as it gave a clear and defined goal and the task was more or less in an "let´s see, if we can do this" 
approach. Combining working structures and group dynamics learned before made the whole environment pleasant.  What I would 
change for the next project is to make finishing the requirements the first priority and then adapting the project around it. 
The troubles we had with the sensors or not having enough pins could have been tackled if attacked earlier.



\textbf{Arthur:}
Participating in the project has been a valuable experience. I learnt through trial and error, how to design my own PCB. Boti, Felix and Henrik helped alot especially if I had any questions. 


\textbf{Casper:}
Write here
\end{document}
