\documentclass[../report.tex]{subfiles}

\begin{document}
    \subsection{Stage division}
    Why divide the project up into multiple smaller stages? It means
    that there will be multiple deadlines, this helps keep the project on
    track. Keeping the project on track in the early stages contributes to the
    final stages where more issues may occur, this mens that there is always a
    working earlier version to showcase if it becomes necessary. It is also
    earlier for both the customer and the development team to see how the
    project will turn out and if there are any design mistakes that have to be
    changed before the final version.

    It is impotent for this method to work, that each stage is clearly defined.
    This ensures that all features for each stage are implemented.

    The below list contests all the requirement of functionalities for each
    stage. It is not a implementation list.

    \textbf{Stage 1: Basic movement}
    \begin{itemize}
        \item The forklift should move unrestricted in any direction.
        \item The forklift should be powered by a battery.
    \end{itemize}

    \textbf{Stage 2: Line following}
    \begin{itemize}
        \item The forklift movement should be restricted to a pre-defined path.
        \item The path should be a line on the floor.
        \item The forklift should stop moving if there is a obstacle in its path.
        \item The forklift platform is solid with no risk of electronic or
        mechanical parts getting loses.
    \end{itemize}

    \textbf{Stage 3: Pallet placement}
    \begin{itemize}
        \item The forks on the forklift should be able to move up and down.
        \item The forklift should be able to pickup a pallet by itself.
        \item The forklift should be able to place a pallet by itself.
        \item The pickup and placement should be in predefined locations.
    \end{itemize}

    The functionalities are not restricted to a specific stage. It is fine that
    if a functionality can be implemented before the begin of its related
    stage.
    The only requirement is that the required functionalities for the current
    stage is completed before the deadline of the stage. 
\end{document}