\documentclass[11pt]{article}
\begin{document}
    \subsection{Forklift related accidents and injuries}
    Forklift related accidents are a common occurrence, both with solid
    stationery objects and moving pedestrians. According to data from "article
    1" there a around 34,000 injuries from forklifts evert year in the US. This
    resolves in lost of work days, that can be expensive for company that may
    need to pat another employ overtime to make of for the lost work.

    Out of 143 incidents with collection with solid objects 75 of them are with
    stationery objects. And 53 of them are collection between forklifts. Both
    of these types of incidents are related to human error, like not paying
    attention to there surrounding then operating forklifts.

    Out of 322 incidents to pedestrians around 50\% of them are incidents are
    the forklifts struck a pedestrians by accident.

    Safety for forklifts can be greatly increased by the use for sensors that
    enables the forklifts to avoid obstacles by it self with the human error
    factor. This is similar to how safety in cars has been greatly improved in
    resent years.

    \subsection{Is there a market for self-driving forklifts?}
    Most company's are always in competition about who can make the best
    product to the lowest cost. One vital part for any company with a physical
    product is the distribution of that product. If it means that a company can
    be more competitive if they reduce there cost for distribution out to the
    retailers. One way this has been done in resent years are to move
    manufacturing and distribution of the product to countries where the
    average salaries are lower. This dose have one major flaw however, it can
    not always be expended that the same quality of work can be done at a lower
    cost. This meant that some company's moved back to there origin. But these
    company's still need to stay somewhat competitive, so there can automation
    of task be a real good investment to a company. Having a warehouse that
    works 24h a day automatic is a great cost reduction, that can help the
    company stay competitive on the price without making compromises on the
    quality.    

    article 1 :Injuries Related to Forklifts and OtherPowered Industrial
    Vehicles inAutomobile  by James W. Collins,
\end{document}